\section{Computing the Time-Step Using Higher-Order DG Schemes}

When making the jump to higher-order DG schemes, we can simply do the same as in the first-order scheme, except we compute the quantities in all of the nodal points instead of using a cell-average. This is valid because the cell-average is a convex combination...\sd{Need to expand on this}. The proof starts with the discretized equation valid at each quadrature point, $q$:
\begin{equation}
    \bU_{q}^{n+1}=\bU_{q}^{n}+\Delta t\,\cL_{q}^{n},
\end{equation}
where $\cL_{q}^{n}$ is a general form of the RHS at time $t^{n}$. If we define a vector $\ol{\bU}\equiv\left(\bU_{1},\cdots,\bU_{q},\cdots,\bU_{Q}\right)^T$, where $Q$ is the total number of quadrature points, and $\ol{\bW}\equiv\left(\bW_{1},\cdots,\bW_{q},\cdots,\bW_{Q}\right)^T$ as a vector of quadrature weights, then we can write the cell-average of $\bU$ as:
\begin{equation}
    \bU_{K}\equiv\ol{\bW}^T\ol{\bU}.
\end{equation}
If we then compute the cell-average of the above equation, we get:
\begin{equation}
    \bU_{K}^{n+1}=\bU_{K}^{n}+\Delta t\,\ol{\bW}^{T}\,\ol{\cL}_{q}^{n}=\ol{\bW}^{T}\left(\ol{\bU}^{n}+\Delta t\,\ol{\cL}^{n}\right)
\end{equation}

\subsection{High-Order Time-Step Restriction for DG}

\blue{NOTE:} This closely follows Jesse's document CFLCondition.pdf.

Consider the one-dimensional system of hyperbolic balance equations:
\begin{equation}\label{Eq:HypBalEqns}
    \pd{\left(\sqrtgm\,\bU\right)}{t}+\pd{\left(\sqrtgm\,\bF^{1}\left(\bU\right)\right)}{1}=\sqrtgm\,\bQ,
\end{equation}
where $\bU$ is a vector of conserved variables, $\bF^{1}\left(\bU\right)$ are the fluxes of those conserved variables in the $x^{1}$-direction, $\bQ$ is a source term, and $\sqrtgm$ is the square-root of the determinant of the spatial three-metric.

We define our reference element by:
\begin{equation}
    I_{j}\equiv\left\{x^{1}:x^{1}\in\left(x^{1}_{L},x^{1}_{H}\right)=\left(x^{1}_{\jmh},x^{1}_{\jph}\right)\right\}.
\end{equation}

We proceed by multiplying \eqref{Eq:HypBalEqns} with $v$, where $v=v\left(x^{1}\right)$ is a test function in the DG scheme, and integrate over the $\jth$ element:
\begin{equation}
    \int_{I_{j}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,v\,dx^{1}+\int_{I_{j}}\pd{\left(\sqrtgm\,\bF^{1}\left(\bU\right)\right)}{1}\,v\,dx^{1}=\int_{I_{j}}\sqrtgm\,\bQ\,v\,dx^{1}.
\end{equation}
We now move the flux term to the RHS and perform integration-by-parts on it, yielding:
\begin{equation}\label{Eq:IntByParts}
    \int_{I_{j}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,v\,dx^{1}=-\left[\sqrtgm\,\hat{\bF^{1}}\,v\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\,v\Big|_{x^{1}_{L}}\right]+\int_{I_{j}}\sqrtgm\,\bF^{1}\,\pd{v}{1}\,dx^{1}+\int_{I_{j}}\sqrtgm\,\bQ\,v\,dx^{1},
\end{equation}
where $\hat{\bF^{1}}$ is a numerical flux.

\blue{NOTE:} $v=1$ is in the space of test functions for the DG method, \textit{and} $v=1$ yields the cell-average when substituted into \eqref{Eq:IntByParts}, therefore the DG method evolves the cell-average.

Substituting $v=1$ into \eqref{Eq:IntByParts} yields:
\begin{equation}\label{Eq:CellAverageDG}
    \int_{I_{j}}\pd{\left(\sqrtgm\,\bU\right)}{t}\,dx^{1}=-\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]+\int_{I_{j}}\sqrtgm\,\bQ\,dx^{1}.
\end{equation}
Note that the volume-term has dropped out because the derivative of a constant is equal to zero.

We define the cell-average of a quantity, $\bX=\bX\left(x^{1},t\right)$, as:
\begin{equation}
    \ol{\bX}\equiv\f{1}{\Delta V_{j}}\int_{I_{j}}\bX\,\sqrtgm\,dx^{1}.
\end{equation}

\red{NEW ASSUMPTION:} We assume that the spatial three-metric is explicitly independent of time. This allows us to pull the metric determinant out of the first integral, yielding for \eqref{Eq:CellAverageDG}:
\begin{equation}
    \f{d\,\ol{\bU}}{dt}=-\f{1}{\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]+\ol{\bQ}.
\end{equation}

\red{NEW ASSUMPTION:} We now specialize this to using the forward-Euler time-stepping algorithm, yielding:

\begin{equation}
    \ol{\bU}^{n+1}=\ol{\bU}^{n}-\f{\Delta t^{n}_{j}}{\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]^{n}+\Delta t^{n}_{j}\,\ol{\bQ}^{n}
\end{equation}
\blue{NOTE:} Since the spatial three-metric is explicitly independent of time, we don't need to specify the time-step at which the volume is computed (i.e. we don't have to write $\Delta V^{n}_{j}$).

Now we define a parameter $\ve\in\left(0,1\right)$ a la \citet{ZS2011b} and re-write the above equation as:
\begin{align}
    \ol{\bU}^{n+1}&=\ve\left\{\ol{\bU}^{n}-\f{\Delta t^{n}_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]^{n}\right\}+\left(1-\ve\right)\left\{\ol{\bU}^{n}+\f{\Delta t^{n}_{j}}{1-\ve}\,\ol{\bQ}^{n}\right\}\\
    &=\ve\,\ol{\bH}_{1}+\left(1-\ve\right)\ol{\bH}_{2},
\end{align}
where
\begin{equation}\label{Eq:H1}
    \ol{\bH}_{1}\equiv\ol{\bU}^{n}-\f{\Delta t^{n}_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{H}}-\sqrtgm\,\hat{\bF^{1}}\Big|_{x^{1}_{L}}\right]^{n},
\end{equation}
and
\begin{equation}
    \ol{\bH}_{2}\equiv\ol{\bU}^{n}+\f{\Delta t^{n}_{j}}{1-\ve}\,\ol{\bQ}^{n}.
\end{equation}
\red{NEW ASSUMPTION:} We assume that $\ol{\bU}^{n}\in\cG$, as defined in \citet{Mignone2005}.

Assuming that $\ol{\bU}^{n}\in\cG$, we now seek to derive the conditions that guarantee $\ol{\bU}^{n+1}\in\cG$.

\subsubsection{The numerical flux term: $\ol{\bH}_{1}$}

We start by numerically computing the cell-average using quadrature with the Gauss-Lobatto quadrature rule. We assume that the DG approximation polynomial for the conserved variables is of order $k$, and that the order of the approximate solution is of order $k+d$, where $d$ is an integer that depends on the metric determinant. For the case of Cartesian coordinates, $d=0$ (because $\sqrtgm\sim x^{0}$), and for spherical-polar coordinates in spherical symmetry, $d=2$ (because $\sqrtgm\sim r^{2}$). Gauss-Lobatto integration will give an exact result if we choose a sufficiently high number, $M$, of quadrature points:
\begin{equation}
    2\,M-3\geq k+d\implies M\geq\f{k+d+3}{2}.
\end{equation}

\blue{NOTE:} We do not use this restriction in the code. We simply take $M$ equal to the number of quadrature points (which is the same as the number of interpolation points). The difference will be accounted for by the presence of the CFL number.

\blue{NOTE:} We now drop the superscript $n$ for the rest of this subsection.

Assuming that we choose a sufficient number of points, we can write the cell-average as:
\begin{align}
    \ol{\bU}=\f{1}{\Delta V_{j}}\sum\limits_{q=1}^{M}w_{q}\,\bU_{q}\,\sqrtgm_{q}\,\Delta x_{j}&=\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{1}\,\bU_{1}\,\sqrtgm_{1}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{M}\,\bU_{M}\,\sqrtgm_{M}\\
    &=\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{1}\,\bU^{+}_{L}\,\sqrtgm_{L}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{M}\,\bU^{-}_{H}\,\sqrtgm_{H},\label{Eq:CellAverageGL}
\end{align}
where $w_{q}$ are the Gauss-Lobatto quadrature weights and $\bU_{q}=\bU\left(x_{q}\right)$, and $\sqrtgm_{q}=\sqrt{\gamma\left(x_{q}\right)}$. The quantity $\bU^{+}_{L}$ refers to the vector of conserved variables evaluated at the lower interface, but on the higher side, so that it is evaluated \textit{in} the $\jth$ cell. Similarly for $\bU^{-}_{H}$.

Our approach is to use the end-points to balance the troublesome terms in the numerical fluxes.

\red{NEW ASSUMPTION:} We now specialize to the local Lax-Friedrichs flux:
\begin{align}
    \hat{\bF}^{1}\Big|_{x^{1}_{L}}&=\hat{\bF}^{1}\left(\bU^{+}_{L},\bU^{-}_{L}\right)=\f{1}{2}\left[\bF^{1}\left(\bU^{+}_{L}\right)+\bF^{1}\left(\bU^{-}_{L}\right)-\alpha_{L}\left(\bU_{L}^{+}-\bU_{L}^{-}\right)\right]\\
    &=\f{1}{2}\left\{-\alpha_{L}\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\alpha_{L}\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right\},
\end{align}
and
\begin{align}
    \hat{\bF}^{1}\Big|_{x^{1}_{H}}&=\hat{\bF}^{1}\left(\bU^{+}_{H},\bU^{-}_{H}\right)=\f{1}{2}\left[\bF^{1}\left(\bU^{+}_{H}\right)+\bF^{1}\left(\bU^{-}_{H}\right)-\alpha_{H}\left(\bU_{H}^{+}-\bU_{H}^{-}\right)\right]\\
    &=\f{1}{2}\left\{-\alpha_{H}\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\alpha_{H}\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right\},
\end{align}
where $\alpha_{H}=\text{max}\left(\alpha_{j},\alpha_{j+1}\right)$ and $\alpha_{L}=\text{max}\left(\alpha_{j-1},\alpha_{j}\right)$ are the largest (in magnitude) wavespeeds as given by the flux-Jacobian.
Now we substitute these expressions along with \eqref{Eq:CellAverageGL} into \eqref{Eq:H1}:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{1}\,\bU^{+}_{L}\,\sqrtgm_{L}+\f{\Delta x_{j}}{\Delta V_{j}}\,w_{M}\,\bU^{-}_{H}\,\sqrtgm_{H}\\
    &-\f{\Delta t_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm_{H}\f{1}{2}\left\{-\alpha_{H}\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\alpha_{H}\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right\}\right]\\
    &+\f{\Delta t_{j}}{\ve\,\Delta V_{j}}\left[\sqrtgm_{L}\f{1}{2}\left\{-\alpha_{L}\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\alpha_{L}\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right\}\right].
\end{align}
Now we combine terms with common factors of the metric determinant:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}}{\Delta V_{j}}\left\{\Delta x_{j}\,w_{1}\,\bU^{+}_{L}+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve}\left(-\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}}{\Delta V_{j}}\left\{\Delta x_{j}\,w_{M}\,\bU^{-}_{H}-\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve}\left(-\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
Next we factor out $\Delta x_{j}$ and the quadrature weights, yielding:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}\,\Delta x_{j}\,w_{1}}{\Delta V_{j}}\left\{\bU^{+}_{L}+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve\,\Delta x_{j}\,w_{1}}\left(-\left[\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}\,\Delta x_{j}\,w_{M}}{\Delta V_{j}}\left\{\bU^{-}_{H}-\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve\,\Delta x_{j}\,w_{M}}\left(-\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
Next we re-write the $\bU^{+}_{L}$ and $\bU^{-}_{H}$ that appear with the flux terms:
\begin{align}
    \bU^{+}_{L}&=2\,\bU^{+}_{L}-\bU^{+}_{L}\\
    \bU^{-}_{H}&=2\,\bU^{-}_{H}-\bU^{-}_{H}.
\end{align}
This gives:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}\,\Delta x_{j}\,w_{1}}{\Delta V_{j}}\left\{\bU^{+}_{L}+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve\,\Delta x_{j}\,w_{1}}\left(-\left[2\,\bU^{+}_{L}-\bU^{+}_{L}-\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}\,\Delta x_{j}\,w_{M}}{\Delta V_{j}}\left\{\bU^{-}_{H}-\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve\,\Delta x_{j}\,w_{M}}\left(-\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[2\,\bU^{-}_{H}-\bU^{-}_{H}+\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
This allows us to write the expression with factors similar to those in \citet{Qin2016}. We find:
\begin{align}
    \ol{\bH}_{1}=&\f{\Delta x_{j}}{\Delta V_{j}}\sum\limits_{q=2}^{M-1}w_{q}\,\bU_{q}\,\sqrtgm_{q}\\
    &+\f{\sqrtgm_{L}\,\Delta x_{j}\,w_{1}}{\Delta V_{j}}\left\{\bU^{+}_{L}\left(1-\f{\Delta t_{j}\,\alpha_{L}}{\ve\,\Delta x_{j}\,w_{1}}\right)+\f{\Delta t_{j}\,\alpha_{L}}{2\,\ve\,\Delta x_{j}\,w_{1}}\left(\left[\bU^{+}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{+}_{L}\right)\right]+\left[\bU^{-}_{L}+\f{1}{\alpha_{L}}\,\bF^{1}\left(\bU^{-}_{L}\right)\right]\right)\right\}\\
    &+\f{\sqrtgm_{H}\,\Delta x_{j}\,w_{M}}{\Delta V_{j}}\left\{\bU^{-}_{H}\left(1-\f{\Delta t_{j}\,\alpha_{H}}{\ve\,\Delta x_{j}\,w_{M}}\right)+\f{\Delta t_{j}\,\alpha_{H}}{2\,\ve\,\Delta x_{j}\,w_{M}}\left(\left[\bU^{+}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{+}_{H}\right)\right]+\left[\bU^{-}_{H}-\f{1}{\alpha_{H}}\,\bF^{1}\left(\bU^{-}_{H}\right)\right]\right)\right\}.
\end{align}
All of the terms in the square brackets are similar the the $\bH$ quantities in \citet{Qin2016} and therefore belong to the set of admissible states, provided that:
\begin{equation}
    \alpha_{L/H}=\alpha^{*}\geq\f{\left|v^{1}\right|\left(h+1-2\,h\,\tau\right)\,W^{2}+\sqrt{\tau^{4}\left(h-1\right)^{2}+\tau^{2}\left(h-1\right)\left(h+1-2\,h\,\tau\right)}}{W^{2}\left(h+1-2\,h\,\tau\right)+\tau^{2}\left(h-1\right)},
\end{equation}
where $h$ is the relativistic specific enthalpy and
\begin{equation}
    \tau\equiv\f{\Gamma-1}{\Gamma},
\end{equation}
where $\Gamma$ is the adiabatic index.

We see that the expressions in the curly brackets are convex combinations (given a restriction on $\Delta t_{j}$), because the coefficients sum to unity. Since the quadrature weights are symmetric (so $w_{1}=w_{M}\equiv w_{GL}$), we find that the condition for $\ol{\bH}_{1}\in\cG$ is a time-step restriction:
\begin{equation}
\Delta t_{j}<\ve\,\Delta x_{j}\,w_{GL}\,\text{min}\left(\f{1}{\alpha_{L}},\f{1}{\alpha_{H}},\f{1}{\alpha^{*}}\right)
\end{equation}
Since we want a time-step that is constant for all elements, we choose:
\begin{equation}
\Delta t<\ve\,w_{GL}\,\text{min}_{j}\left(\f{\Delta x_{j}}{\text{max}\left(\alpha_{L},\alpha_{H},\alpha^{*}\right)}\right).
\end{equation}

\red{NEW ASSUMPTION:} In order for this to work, we also demand that all of the $\bU_{q}$ are within physical bounds.

\blue{NOTE:} We see the effect of the high-order approximation in the presence of the quadrature end-point weight $w_{GL}$. As the order increases, $w_{GL}$ decreases, thus making a tighter restriction on the time-step.

\blue{NOTE:} It is worth noting that this result is \textit{not} independent of the metric, because it is incorporated through the wave-speed in the numerical flux.
